---
title: "Fb_troll_2_final"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

## Sanchit Soni
This is the the second survey which consisted the following questions like-
Which gender gets trolled by which other gender?
Which gender gets more emotionally hurt?
Which gender gets more angered  by trolling?






```{r import, echo=F}
data <- read_csv("fb_troll2.csv")
data %>% head
# First two rows (after the column name) have metadata, remove them
data <- data %>% filter(row_number() > 2)
# add row ids
data <- data %>% rownames_to_column("id")
data %>% head
```


## Which gender gets trolled by which other gender?
1= Male 2= Female 4= Don't remember 5=Never been trolled

```{r}

library(reshape2)
mmff <- dcast(data %>% select(Q3, Q5), Q3 ~ Q5)
filter(data, Q5=="1"|Q5=="2")
print (mmff)
```


```{r}
 
# Library
library(fmsb)
 
# Create data: note in High school for several students
rradar <- matrix(c(10,1,3,15,4,3,1,13),ncol=4,byrow=TRUE)
colnames(rradar) <- c("Male","Female", "DR", "NBT")
rownames(rradar) <- c("m","f")
rradar <- as.table(rradar)
rradar
 
heat_matrix <- data.matrix(rradar)

malefemale_heatmap <- heatmap(heat_matrix, Rowv=NA, Colv=NA, col = heat.colors(256), scale="none", margins=c(10,5))
 
 
```


```{r}
library(plotly)
packageVersion('plotly')

p <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  ) %>%
  add_trace(
    r = c(10, 1, 0, 3, 15, 10),
    theta = c('Male','Female','Other', 'CR', 'NBT', 'Male'),
    name = 'Male'
  ) %>%
  add_trace(
    r = c(4, 3, 0, 1, 13, 4),
    theta = c('Male','Female','Other', 'CR', 'NBT', 'Male'),
    name = 'Female'
  ) %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,20)
      )
    )
  )
print(p)
```



## Which gender gets more emotionally hurt?


```{r}
data <- data %>% mutate_at(vars(starts_with("Q2_1")), as.numeric)
data <- data %>% mutate(emo_hurt=
(6-Q2_1))
data %>% select(emo_hurt, starts_with("Q2_1"))
```







```{r}
library(glue)
# define function to output 95% confidence interval (z-score = 1.96) string
ci95 <- function(x) {
glue("({format(mean(x)-1.96*sd(x), digits=3)}, {format(mean(x)+1.96*sd(x), digits=
3)})")
}
data %>% summarise(mean=mean(emo_hurt),
SD=sd(emo_hurt),
CI=ci95(emo_hurt))
```                            
##I am interested in whether there is a difference in emotional hurt scores between females and males.
```{r}
desc <- data %>% group_by(Q3) %>% summarise(mean=mean(emo_hurt),
SD=sd(emo_hurt),
CI=ci95(emo_hurt))
desc

``` 

```{r}
males <- data %>% filter(Q3 == 1) %>% pull(emo_hurt)
females <- data %>% filter(Q3 == 2) %>% pull(emo_hurt)
data %>% filter(Q3 == 1) %>% ggplot(aes(emo_hurt)) + geom_histogram(binwidth=2)

``` 

```{r}
data %>% filter(Q3 == 2) %>% ggplot(aes(emo_hurt)) + geom_histogram(binwidth=2)

``` 




```{r}
t.test(males, females, var.equal=T)

``` 

## Which gender gets more angered  by trolling?


```{r}
data <- data %>% mutate_at(vars(starts_with("Q2_2")), as.numeric)
data <- data %>% mutate(deg_anger=
(6-Q2_2))
data %>% select(deg_anger, starts_with("Q2_2"))
```



```{r}
library(glue)
# define function to output 95% confidence interval (z-score = 1.96) string
ci95 <- function(x) {
glue("({format(mean(x)-1.96*sd(x), digits=3)}, {format(mean(x)+1.96*sd(x), digits=
3)})")
}
data %>% summarise(mean=mean(deg_anger),
SD=sd(deg_anger),
CI=ci95(deg_anger))
```




```{r}
desc2 <- data %>% group_by(Q3) %>% summarise(mean=mean(deg_anger),
SD=sd(deg_anger),
CI=ci95(deg_anger))
desc2
```


```{r}
males <- data %>% filter(Q3 == 1) %>% pull(deg_anger)
females <- data %>% filter(Q3 == 2) %>% pull(deg_anger)
data %>% filter(Q3 == 1) %>% ggplot(aes(deg_anger)) + geom_histogram(binwidth=2)

```

```{r}
data %>% filter(Q3 == 2) %>% ggplot(aes(deg_anger)) + geom_histogram(binwidth=2)

```

```{r}
t.test(males, females, var.equal=T)

```

```{r}


```