---
title: "Final data project: Facebook trolling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

## Introduction
The first step was to collect data through a survey on Facebook trolling. I got a total of 57 responses.



```{r import, echo=F}
data <- read_csv("fb_troll.csv")
data %>% head
# First two rows (after the column name) have metadata, remove them
data <- data %>% filter(row_number() > 2)
# add row ids
data <- data %>% rownames_to_column("id")
data %>% head
```
## 2. Data Columns
Let's now see what the columns of our data set are. Note that the first 17 columns are metadata that Qualtrics inserted. 
```{r}
colnames(data)
```
##Facebook Analysis
See how many people have experienced trolling
```{r warning=FALSE}
data %>% group_by(Q1) %>% count
ggplot(data, aes(data$Q1)) + geom_bar()
```
```{r warning=FALSE}
# create Q1_num
data <- data %>% mutate(Q1_num=as.numeric(Q1)) 

# show unsuccessful conversions
invalid_ids <-  data %>% filter(is.na(Q1_num)) %>% pull(id)
data %>% filter(is.na(Q1_num)) %>% select(id,Q1,Q1_num)
``` 


```{r warning=FALSE}
data %>% group_by(Q2) %>% count
ggplot(data, aes(data$Q2)) + geom_bar()
```


```{r warning=FALSE}
 
data %>% group_by(Q3) %>% count
data %>% filter(Q3 != "") %>% ggplot(aes(Q3)) + geom_bar()

```


```{r warning=FALSE}
data %>% drop_na()
data %>% group_by(Q10) %>% count
ggplot(data, aes(data$Q10)) + geom_bar()
```

```{r warning=FALSE}
heatmap_1 <- matrix(c(14,10,26,12,8,17),ncol=3,byrow=TRUE)
colnames(heatmap_1) <- c("PR","CR", "Report")
rownames(heatmap_1) <- c("Male","Female")
heatmap_1 <- as.table(heatmap_1)
heatmap_1
```
```{r warning=FALSE}
heat_matrix <- data.matrix(heatmap_1)
```


##Heatmap

Here I was trying to create a Heatmap to see patterns between Male-Female and who reported more than the other, and if male or female faced personal remark/community remark more than the other person.
```{r warning=FALSE}
malefemale_heatmap <- heatmap(heat_matrix, Rowv=NA, Colv=NA, col = heat.colors(256), scale="none", margins=c(5,5))
```

##Total time 

I was interested in doing some kind of t test to see which group Male or Female spends more time on Facebook. To do that, I converted new column which stores average number of times people login to their Fb account. I created another column which has total time spent by people each time they logged in. I then multipiled the two to get the total time spent with male/female ratio. Then, I ran t test.

```{r warning=FALSE}
data <- data %>%
  mutate(Q3_num = case_when(Q3 == "10-12 times a day" ~ "11",
                            Q3 == "Once a day" ~ "1",
                            Q3 == "1-3 times a day" ~ "1.5",
                            Q3 == "Once a week" ~ "0.14",
                            Q3 == "I don't keep a track" ~ "0",
                            Q3 == "" ~ "0",
                            Q3 == "NA" ~ "0"))
data <- data %>%
  mutate(Q5_num = case_when(Q5 == "1-5 minutes (Quickly checking notifications)" ~ "2.5",
                            Q5 == "An hour" ~ "60",
                            Q5 == "1-3 times a day" ~ "1.5",
                            Q5 == "10-15 minutes" ~ "12.5",
                            Q5 == "It really depends on the day" ~ "0",
                            Q5 == "I have no idea" ~ "0",
                            Q5 == "" ~ "0",
                            Q5 == "NA" ~ "0"))
  
```


#Descriptive statistics for how many times Fb was accessed in a day

```{r warning=FALSE}
data <- data %>% drop_na(Q3_num) %>% mutate(Q3_num=as.numeric(Q3_num))
data <- data %>% drop_na(Q5_num) %>% mutate(Q5_num=as.numeric(Q5_num))
data <- data %>% mutate(total_time = Q3_num * Q5_num)
```


```{r warning=FALSE}
data %>% summarise(Q3_mean = mean(Q3_num),
Q3_median = median(Q3_num),
Q3_min = min(Q3_num),
Q3_max = max(Q3_num),
Q3_total = n(),
Q3_sd = sd(Q3_num))

```
```{r warning=FALSE}
ggplot(data %>% transmute(Q3_num=sqrt(Q3_num)), aes(Q3_num)) + geom_histogram(binwidth=1) #coord_cartesian(xlim=c(0,3100),ylim=c(0,15))
```
For those who only identify themselves as Females 

```{r warning=FALSE}
females <- data %>% filter(Q7 == "Female") %>% mutate(Q3_num=log(Q3_num))
ggplot(females, aes(Q3_num)) + geom_histogram(binwidth=1)+ coord_cartesian(xlim=c(0,
10),ylim=c(0,10))
```

For those who only identify themselves as Mmales 

```{r warning=FALSE}
males <- data %>% filter(Q7 == "Male") %>% mutate(Q3_num=log(Q3_num))
ggplot(males, aes(Q3_num)) + geom_histogram(binwidth=1)+ coord_cartesian(xlim=c(0,
10),ylim=c(0,10))
```

#Descriptive statistics for how much time was spent on Fb each time that a person logged in (time in minutes)

```{r warning=FALSE}
data %>% summarise(Q5_mean = mean(Q5_num),
Q5_median = median(Q5_num),
Q5_min = min(Q5_num),
Q5_max = max(Q5_num),
Q5_total = n(),
Q5_sd = sd(Q5_num))
```


```{r warning=FALSE}
ggplot(data %>% transmute(Q3_num=sqrt(Q3_num)), aes(Q3_num)) + geom_histogram(binwidth=1) #coord_cartesian(xlim=c(0,3100),ylim=c(0,15))
```

For those who qualify themselves as females 

```{r warning=FALSE}
females <- data %>% filter(Q7 == "Female") %>% mutate(Q5_num=log(Q5_num))
ggplot(females, aes(Q5_num)) + geom_histogram(binwidth=1)+ coord_cartesian(xlim=c(0,
10),ylim=c(0,10))

```

For those who qualify themselves as males 
```{r warning=FALSE}
males <- data %>% filter(Q7 == "Male") %>% mutate(Q5_num=log(Q5_num))
ggplot(males, aes(Q5_num)) + geom_histogram(binwidth=1)+ coord_cartesian(xlim=c(0,
10),ylim=c(0,10))
```

#Descriptive statistics for how much time was spent on Fb

```{r warning=FALSE}
data %>% summarise(t_mean = mean(total_time),
t_median = median(total_time),
t_min = min(total_time),
t_max = max(total_time),
t_total = n(),
t_sd = sd(total_time))
```


```{r warning=FALSE}
ggplot(data %>% transmute(total_time=sqrt(total_time)), aes(total_time)) + geom_histogram(binwidth=1) #coord_cartesian(xlim=c(0,100),ylim=c(0,20))
```


Now running t test to see who uses more facebook between males and females

```{r}
female <- data %>% filter(Q7 == "Female")
male <- data %>% filter(Q7 == "Male")
male_tt <- male %>% pull(total_time)
female_tt <- female %>% pull(total_time)
t.test(male_tt,female_tt,var.equal=TRUE)
```



```{r}
megaplot <- data %>% select(Q7,Q3_num, Q5_num, total_time)
```

```{r}
print(megaplot)
```
```{r}

library(GGally)

ggparcoord(megaplot, columns = 1:4, groupColumn = 'Q7', scale = 'globalminmax')

```



```{r}
# group by combinations and count
#megaplot %>% group_by(Q7) %>% count()

# set an id string that denotes the value combination
megaplot %>% mutate(id = factor(paste(Q3_num, Q5_num, total_time, Q7, sep = '-')))

megaplot2 <- megaplot %>% mutate(id = factor(paste(Q3_num, Q5_num, total_time, Q7, sep = '-')))
```
```{r}
head(megaplot2, n=31)
```

```{r}

library(GGally)

ggparcoord(megaplot2, columns = 2:4, groupColumn = 'id', scale = 'uniminmax', missing = 'exclude', title = "Parallel Coordinate Plot for Male-Female total times logged in, time spent during each logged session and total time ")

```

```{r}
mp3<- as.data.frame(megaplot2)
library(ggparallel)
ggparallel(list('Q7','total_time', 'Q3_num', 'Q5_num'), mp3, order = 0)
```






This is the end of results-----------------